Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-09-28 docs/Manuscript.tex
Updated methos, still need to include Johns comments, finalize empirical specification and proof read

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\usepackage[normalem]{ulem}
% avoid problems with \sout in headers with hyperref:
\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-09-27}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1} Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara, CA
\textsuperscript{2} Department of Economics, University of Hawaii at
Manoa, Honolulu, HI}

\usepackage{float}
\floatplacement{figure,table}{H}

@@

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\section{To do}\label{to-do}

\begin{itemize}
\tightlist
\item
  {[}x{]} Divide pipa vessels by type of boat (longline vs.~purse seine)
\item
  {[}x{]} Identify two counterfactuals:

  \begin{itemize}
  \tightlist
  \item
    {[}x{]} A: PNA, similar vessel, never fished inside PIPA
  \item
    {[} {]} \sout{B: Taiwan, Never in PNA, Similar region}
  \end{itemize}
\item
  {[}x{]} Change in fishing hours before vs after
\item
  {[} {]} \sout{Change in total hours before vs after}
\item
  {[} {]} Change in distance before vs after
\item
  {[}x{]} Where do PIPA vessels go?
\item
  {[}x{]} Make sure I have full tracks of all mmsis
\end{itemize}

@@

The current approach is to estimate what percentage of fishing effort
from the PNA was displaced by PIPA and use this to infer something about
Palau. While this provides a measure of the displacement, it does not
fully address the possibility of costs increasing. I believ we can use
individual tracks (as opposed to just the gridded effort) and obtain
show how their behavior changed (\emph{i.e.} are they fishing further
away, are they fishing more, where are they now?).

\subsubsection{Model specifications}\label{model-specifications}

Our model specification uses a DiD approach. In this case, we interact
the before-after dummy with a treatment dummy. The treatment and control
groups follow our definition in the data description. The model takes
the form of:

\[
H_{ijkl} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \gamma_l+ \epsilon_{ijk}
\]

Where \(\mu_j\), \(\phi_k\), and \(\gamma_l\) represent month-, year-,
and flag-level fixed effects. I use total hours at the vessel-month
level.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\subsection{Purse seiners}\label{purse-seiners}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:puse}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

@@

\subsection{Longliners}\label{longliners}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{\label{fig:unnamed-chunk-11}\label{fig:long}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-09-27}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara, CA
\textsuperscript{2}Department of Economics, University of Hawaii at
Manoa, Honolulu, HI}

\usepackage{float}
\floatplacement{figure,table}{H}
\usepackage{lineno}
\linenumbers

@@

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\clearpage

@@

\subsubsection{Change in behavior}\label{change-in-behavior}

The first analysis focuses on identifying the response of fishing
vessels to PIPA closure. Our variables of interests are fishing effort,
indicated by total fishing hours per month, and distance traveled (Km)
on every fishing trip. We compare fishing hours\footnote{And soon,
  distance} before and after the implementation of PIPA using a
Difference-in-Differences approach, where we track the variable of
interest for vessels that used to fish inside PIPA and vessels that
never fished inside PIPA, before and after PIPA implementation. Our
specification is the following:

\[
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{i,t}
\]

Where \(y_{ijkl}\) is the variable of interest for vessel \(i\) in time
period \(t\). A dummy variable \(Post_i\) takes the value of 0 for all
dates prior to PIPA implementation and a value of 1 por all dates
including and following PIPA implementation. \(Treat_i\) is a dummy
variable indicating whether a vessel belongs to the control
(\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
the standard intercept, \(\beta_1\) captures the \emph{ex post} change,
\(\beta_2\) captures the difference between treated and control groups,
and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
the treatment effect. Finally, \(\mu_t\), \(\phi_t\), and \(\gamma_i\)
represent month-, year-, and flag-level dummies that account for
seasonality or country-level management interventions.

\subsubsection{Vessel displacement and
redistribution}\label{vessel-displacement-and-redistribution}

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figure
\ref{fig:redist_trend}. EEZs that had sproadic fishing events were
pooled into a group of ``others'', leaving us with a total of n = 12
spatially defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'').
Figure \ref{fig:redist_trend_spa} shows the yearly average of the
relative spatial allocation of fishing efforts; this is the spatial
representation of \ref{fig:redist_trend} averaged by year.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:redist_trend}}
\end{figure}

To evaluate this change in effort allocation, we regress our variable of
interest, fishing hours, on the interaction between a dummy variable
indicating the policy intervention and a dummy variable for countries,
to obtain the by-country change in proportional allocation of fishing
effort:

\[
y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
\]

Our variable of interest, \(y_{i,t}\) represents the proportion of
fishing hours that country \(i\) receives at time \(t\). \(Post\) also
represents a policy dummy that takes the value of 0 for all dates before
implementation of PIPA, and 1 otherwise. \(Country\) is a dummy variable
for countries, interpreted as individual EEZs, the high seas, and a
group of ``other EEZs''. Our parameter of interest is \(\beta_3\), which
captures the country-level change in proportional fishing effort.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\subsection{Change in behavior}\label{change-in-behavior-1}

\subsubsection{Purse seiners}\label{purse-seiners}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{\label{fig:unnamed-chunk-13}\label{fig:puse}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

@@

\subsubsection{Longliners}\label{longliners}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:long}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

\subsection{Effort displacement and
redistribution}\label{effort-displacement-and-redistribution}

\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}

### 2018-09-28 rmd/Manuscript.Rmd
Updated methos, still need to include Johns comments, finalize empirical specification and proof read

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
subtitle: "Updated on `r Sys.Date()`"
author: |
  Juan Carlos Villaseñor-Derbez^1^
  John Lynham^2^
abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years. Fishing effort is effectively eliminated within these protected areas upon implementation. The benefits of reducing effort have been largely studied, and include increases in abundance, biomass, and diversity within the bounded regions. These no-take zones may produce spillover effects, which provide fish for outside areas. However, the economic and ecological implications of displacing fishing effort are not yet fully understood. Novel data products that track fishing effort at the vessel-level allow us to identify changes in fleet- and vessel-level behavior upon the implementation of protected areas, as well as how these redistribute. This papers evaluates the implications of implementing LSMPA, by evaluating changes in fishing hours, showing that vessels in the effected region reduce fishing effort after the implementation of PIPA. Our results are robust to a set of specifications. We also track the relative spatial allocation of fishing events thorugh time, and identify that areas closer to PIPA show an increase in relative fishing hourse due to the displacement of PIPA-fishing vessels. Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications."
date: |
  ^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA
  ^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI
output:
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 4
    citation_package: natbib
    keep_tex: yes
    number_sections: no
header-includes:
  - \usepackage{float}
  - \floatplacement{figure,table}{H}
bibliography: references.bib
biblio-style: nature
---

```{r, echo = F, message = F, warning = F}
suppressPackageStartupMessages({
  library(startR)
  library(tidyverse)
})

@@

options(knitr.table.format = "latex")
```

@@

$$
y_{i,t} = \alpha + \beta Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{it}
$$

Where $y_{ijkl}$ is the variable of interest for vessel $i$ in time period $t$. $\alpha$ is the standard intercept, and $\beta$ is our parameter of interest: de DiD estimate capturing the treatment effect. A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation date. $Treat_i$ is a dummy variable indicating whether a vessel belongs to the control ($Treat_i = 0$) or treatment ($Treat_i = 1$) group. Finally, $\mu_t$, $\phi_t$, and $\gamma_i$ represent month-, year-, and flag-level dummies that account for seasonality or country-level management interventions.

@@

<!-- $$ -->
<!-- H_{ijk} = \alpha + \beta Post_i + \mu_j + \phi_k + \epsilon_{ijk} -->
<!-- $$ -->

<!-- Where $H_{ijk}$ is a measure of effort (*.i.e.* total hours, fishing hours, distance traveled), $\beta$ captures the change for before ($Post_i = 0$) and after ($Post_i = 1$) implementation of PIPA, $mu_j$ captures the month fixed-effects, and $\phi_k$ captures vessel-level fixed-effects. We use this general model and the nested specifications which drop the month and vessel-level fixed effects to test for differences. -->

@@

@@

## Purse seiners

@@

## Longliners

@@

>>>>

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
subtitle: "Updated on `r Sys.Date()`"
author: |
  Juan Carlos Villaseñor-Derbez^1^
  John Lynham^2^
abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years. Fishing effort is effectively eliminated within these protected areas upon implementation. The benefits of reducing effort have been largely studied, and include increases in abundance, biomass, and diversity within the bounded regions. These no-take zones may produce spillover effects, which provide fish for outside areas. However, the economic and ecological implications of displacing fishing effort are not yet fully understood. Novel data products that track fishing effort at the vessel-level allow us to identify changes in fleet- and vessel-level behavior upon the implementation of protected areas, as well as how these redistribute. This papers evaluates the implications of implementing LSMPA, by evaluating changes in fishing hours, showing that vessels in the effected region reduce fishing effort after the implementation of PIPA. Our results are robust to a set of specifications. We also track the relative spatial allocation of fishing events thorugh time, and identify that areas closer to PIPA show an increase in relative fishing hourse due to the displacement of PIPA-fishing vessels. Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications."
date: |
  ^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA
  ^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI
output:
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 4
    citation_package: natbib
    keep_tex: yes
    number_sections: no
header-includes:
  - \usepackage{float}
  - \floatplacement{figure,table}{H}
  - \usepackage{lineno}
  - \linenumbers
bibliography: references.bib
biblio-style: nature
---

```{r, echo = F, message = F, warning = F}
suppressPackageStartupMessages({
  library(startR)
  library(sf)
  library(tidyverse)
})

@@

options(knitr.table.format = "latex")

source(here::here("scripts", "st_rotate.R"))
source(here::here("scripts", "sfc_as_cols.R"))
```

@@

$$
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{i,t}
$$

Where $y_{ijkl}$ is the variable of interest for vessel $i$ in time period $t$. A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation. $Treat_i$ is a dummy variable indicating whether a vessel belongs to the control ($Treat_i = 0$) or treatment ($Treat_i = 1$) group. $\alpha$ is the standard intercept, $\beta_1$ captures the *ex post* change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect. Finally, $\mu_t$, $\phi_t$, and $\gamma_i$ represent month-, year-, and flag-level dummies that account for seasonality or country-level management interventions.

@@

@@

```{r}
displacement_data <- readRDS(file = here::here("data", "displacement_data.rds"))
```

Our second part of the analyses focuses on the redistribution of fishing effort. In other words, identifying where do vessels that used to fish inside PIPA go after its establishment. We calculate the monthly relative distribution of fishing hours by all treated vessels across all fished EEZs and the high seas. These trends are shown in Figure \ref{fig:redist_trend}. EEZs that had sproadic fishing events were pooled into a group of "others", leaving us with a total of n = `r length(unique(displacement_data$country))` spatially defined regions (*i.e.* EEZs, High Seas, "other EEZs"). Figure \ref{fig:redist_trend_spa} shows the yearly average of the relative spatial allocation of fishing efforts; this is the spatial representation of \ref{fig:redist_trend} averaged by year.

<!-- Explicar cuales EEZs habia en total y cuales quedaron en un pie de nota o algo asi -->

```{r}
country_groups <- c("COK", "FSM", "KIR", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV")

eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"), layer = "EEZ_subset")

pipa <- read_sf(dsn = here::here("data", "spatial", "PIPA"),
                layer = "PIPA") %>% 
  mutate(inside = T) %>% 
  select(inside) %>% 
  st_rotate()
```

```{r, fig.cap = "\\label{fig:redist_trend}"}
displacement_data %>% 
  ggplot(aes(x = date, y = h_prop, group = post)) +
  geom_smooth(method = "lm") +
  geom_point() +
  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
  scale_fill_brewer(palette = "Paired") +
  ggtheme_plot() +
  facet_wrap(~country, scales = "free_y")
```

```{r, fig.cap = "\\label{fig:redist_trend_spa}Proportion of fishing hours that all vessels spent on each of the EEZs and the high seas.", eval = F}
pipa_map_disp <- pipa %>% 
  mutate(country = "PIPA") %>% 
  left_join(displacement_data, by = "country")

# Los colores del mapa deben estar dados por el Post:Country
eez %>% 
  left_join(displacement_data, by = c("ISO_Ter1" = "country")) %>%
  group_by(year) %>% 
  summarize(h_prop = mean(h_prop, na.rm = T)) %>% 
  ggplot() +
  geom_sf(aes(fill = h_prop, linetype = PNA), size = 1, color = "black") +
  geom_sf(data = pipa_map_ba_disp, aes(fill = h_prop), linetype = "dashed", color = "red") +
  ggtheme_plot() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(10)) +
  facet_wrap(~year)
```

<!-- Meter tabla ba_disp aqui -->

To evaluate this change in effort allocation, we regress our variable of interest, fishing hours, on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries, to obtain the by-country change in proportional allocation of fishing effort:

$$
y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
$$

Our variable of interest, $y_{i,t}$ represents the proportion of fishing hours that country $i$ receives at time $t$. $Post$ also represents a policy dummy that takes the value of 0 for all dates before implementation of PIPA, and 1 otherwise. $Country$ is a dummy variable for countries, interpreted as individual EEZs, the high seas, and a group of "other EEZs". Our parameter of interest is $\beta_3$, which captures the country-level change in proportional fishing effort.

@@

## Change in behavior

### Purse seiners

@@

### Longliners

@@

## Effort displacement and redistribution

```{r}
ba_disp <- displacement_data %>% 
  group_by(country, post) %>% 
  summarize(h_prop_m = mean(h_prop)) %>% 
  spread(post, h_prop_m) %>% 
  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
  select(country, change)

pipa_map_ba_disp <- pipa %>% 
  mutate(country = "PIPA") %>% 
  left_join(ba_disp, by = "country")

# Los colores del mapa deben estar dados por el Post:Country
eez %>% 
  left_join(ba_disp, by = c("ISO_Ter1" = "country")) %>%
  filter(!is.na(change)) %>% 
  ggplot() +
  geom_sf(aes(fill = change), size = 1, color = "black") +
  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
  ggtheme_plot() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
```

```{r, eval = F}
# Dont have this here. Just write the model specification

displacement_data %>% 
  filter(!is.na(country)) %>% 
  lm(h_prop ~ post*country, data = .) %>% 
  summary()
```
